Comb associative operads

### 2018-07-20 Magmatic_operads.tex
Ajout preuve de l'injectivité de \Oca

\begin{Theorem} \label{thm:lattice_structure_of_QMag}
    The tuple $\LatQMag$ is a lattice.
\end{Theorem}
\begin{proof}
  The map $\Oca:\IMag\to\QMag$ defined by $\Oca(I) := \KMag/_I$ is a
  bijection by definition of $\QMag$. Moreover, from
    Proposition~\ref{prop:order_relations_on_QMag_and_ideals},
    $\Oca_2\OrdQMag\Oca_1$ is equivalent to $I_1\subseteq I_2$, so that
    $\left(\QMag,\OrdQMag\right)$ is a poset and $\Oca$ is a decreasing
    bijection. The tuple $\left(\IMag,\subseteq,\cap,+\right)$ being a
    lattice, the decreasing bijection $\mathcal{Q}$ induces lattice
    operations on $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by
    definition.
\end{proof}
\medbreak

>>>>

\begin{Theorem} \label{thm:lattice_structure_of_QMag}
  The tuple $\LatQMag$ is a lattice.
\end{Theorem}
\begin{proof}
  First, we observe that the map $\Oca:\IMag\to\QMag$ defined by
  $\Oca(I) :=\KMag/_I$ is a bijection: it is surjective by definition of
  $\QMag$ and it is injective since $\Oca(I_1)=\Oca(I_2)$ implies that
  the kernel of the natural projection $\KMag\to\Oca(I_1)=\Oca(I_2)$ is
  both equal to $I_1$ and $I_2$. Moreover, from
  Proposition~\ref{prop:order_relations_on_QMag_and_ideals},
  $\Oca_2\OrdQMag\Oca_1$ is equivalent to $I_1\subseteq I_2$, so that
  $\left(\QMag,\OrdQMag\right)$ is a poset and $\Oca$ is a decreasing
  bijection. The tuple $\left(\IMag,\subseteq,\cap,+\right)$ being a
  lattice, the decreasing bijection $\Oca$ induces lattice operations on
  $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by definition.
\end{proof}
\medbreak
